\documentclass{JAC2003}
% IPAC 2012 - General document layout
\usepackage[utf8]{inputenc}
\usepackage{graphicx, subfigure,amsmath}
\usepackage{booktabs}


\begin{document}
\title{Evaluation of the Beam Coupling Impedance of New Beam Screen Designs for the LHC Injection Kicker Magnets}
\author{H. Day\thanks{hugo.day@hep.manchester.ac.uk}$^{\dagger\ddagger\star}$, M.J. Barnes$^{\dagger}$, F. Caspers$^{\dagger}$, R.M. Jones$^{\ddagger \star}$, E. Métral$^{\dagger}$, B. Salvant$^{\dagger}$ \\
$\dagger$ CERN, Switzerland \\
$\ddagger$ School of Physics and Astronomy, The University of Manchester, Manchester, UK \\
$\star$ Cockcroft Institute, Daresbury, UK \\}

\maketitle

\begin{abstract}
The LHC injection kicker magnets (MKIs) have experienced a significant degree of beam induced heating since the beginning of the 2011 due to the increasing intensity stored in the LHC, for long periods of time, and the relatively large broadband impedance of the installed kicker magnets. In this paper we show the sources of impedance in the MKIs, especially the effect that the beam screen dimensions have on the impedance. We show how these alter the power loss, and present an improved beam screen design that improves shielding on the magnet, whilst further improving electrical breakdown.
\end{abstract}

%Title format - Title; Authors; Affiliation; conference
%Abstract - Copied from submitted abstract (maybe changed to represent changes in presented paper)
%Introduction
%Body of data
%Conclusion
%Acknowledgements
%References

% Aim of paper - To present the causes of the beam coupling impedance in the beam screen - length of overlap, thickness, screening by conductors. Expected power loss for the new screen design with present and HL-LHC parameters
% Sections:
% Introduction - Brief history of the MKI heating - reference to Mike's paper last year and this year
% Reasons for the impedance - Distinction between well screened and not well screened
% - Increasing number of screen conductors reduces effect of the ferrite
% - Dimensions of the capacitive end changing impedance profile
% - Effect of different ferrites on the 30-40MHz peak if time
% Power loss expectactions for HL-LHC, post LS1 between 15, 19 and New design
%
%
%

% Images to include
% New screen design cross section
% New screen design impedance
% Various lengths of overlap impedance and predicted resonant frequency
% 

\section{INTRODUCTION}

During the 2011 and 2012 runs of the LHC, high temperatures were observed in several devices in the LHC  \cite{metral_cham2012}, a critical piece being the LHC injection kicker magnets (MKIs), which were attributed to beam-induced heating due to high power loss from the interaction of the circulating beam with the beam coupling impedance of the MKI. This heating was observed to raise the temperature of the ferrite yoke of the kickers above their Curie point during fills, thereby necessitating long waiting times for the ferrite to cool before safe injection could be carried out \cite{mki-heating}. 

In response to this an extensive study in reducing the temperature of the ferrite yoke was carried out, aimed at reducing the power loss into the kicker magnet and increasing the transfer of thermal energy from the ferrite yoke to the surroundings. A new beam screen was implemented in MKI8d in technical stop 3 (23/09/12-27/09/12) with improved screening of the ferrite from the beam and some modifications to reduce the liklihood of electrical breakdown during magnet pulsing was installed, and was observed to greatly reduce the temperature of the ferrite yoke \cite{mki-heatingTemp}. Building on this success, more 


\section{CAUSES OF THE IMPEDANCE}

\section{NEW BEAM SCREEN DESIGN}

\section{POWER LOSS FOR FUTURE OPERATION}

\section{SUMMARY}

\begin{thebibliography}{9}

\bibitem{mki-heating}
\emph{"Analysis of Measured Ferrite Heating of the LHC Injection Kickers and Proposals for Future Reduction of Temperature"}, M.J. Barnes, L. Ducimetière, N. Garrel, B. Goddard, W. Weterings, IPAC'12, New Orleans, USA, 2012.

\bibitem{mki-heatingTemp}
\emph{"Beam Induced Ferrite Heating of the LHC Injection Kickers and Proposals for Improved Cooling"}, M.J. Barnes, S. Calatroni, F. Caspers, L. Ducimetière, M. Garlasché, V. Gomes Namora, N. Magnin, V. Mertens, Z.K. Sobiech, M. Taborelli, J. Uythoven, W. Weterings, these proceedings.

\bibitem{beam-screen}
\emph{"An Improved Beam Screen for the LHC Injection Kickers"}, M.J. Barnes, F. Caspers, L. Ducimetière, N. Garrel. T. Kroyer, PAC'07, Alberquerque, USA, 2007.

\bibitem{cst-cite}
\texttt{http://www.cst.com}.

\bibitem{kicker_meas}
\emph{"Coaxial Wire Measurements of Ferrite Kicker Magnets"}, H. Day, M. J. Barnes, F. Caspers, E. Métral, B. Salvant, C. Zannini, R.M. Jones, IPAC'11, San Sebastian, 2011, MOPS078.

\bibitem{metral_cham2012}
\emph{Beam-Induced Heating/Bunch Length/RF and Lessons for 2012}, E. Metral et al, LHC Performance Workshop, Chamonix 2012. 


\end{thebibliography}
\end{document}

